### 2020-04-08 paper/UCOR.tex
Changed 'One of the first...'

One of the first successful uses of the \ac{UC} framework was a model
created by Jan Camenish and Anna Lysyanskaya (a model we will call the
CL-model). This model was an attempt at formalising the concept of
onion routing using the UC-framework. It relied on an ideal
functionality, and five properties that ensured a protocol would properly
simulate the ideal functionality~\cite{CL-model}. We will however not
use these five original properties, rather opting to use three newer
properties~\cite{kuhn}.

>>>>

One  successful use of the \ac{UC} framework is a model
created by Jan Camenish and Anna Lysyanskaya (a model we will call the
CL-model). This model is an attempt at formalising the concept of
onion routing using the UC-framework. It relies on an ideal
functionality, and five properties that ensures a protocol would properly
simulate the ideal functionality~\cite{CL-model}. We will however not
use these five original properties, rather opting to use three newer
properties~\cite{kuhn}.
